---
title: "Lego Analysis"
author: "Paweł Śnioszek"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: spacelab
    number_sections: yes
  pdf_document:
    toc: yes
---

```{r setup, echo = F}
knitr::opts_chunk$set(
  echo = FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE
)
```

# Executive summary

TODO - write executive summary

# Libraries

Libraries used to prepare the report.

```{r libraries, echo = TRUE}
library(knitr)
library(dplyr)
library(R.utils)
library(data.table)
library(tools)
library(stringr)
library(ggplot2)
library(plotly)
library(tidyr)
library(scales)
```

# Data loading

Code to load datasets from compressed files stored in a specified folder.

```{r data_load, cache = TRUE, echo = T}
folder_name = "data"
csv_files <- list.files("data",
                        pattern = "\\.csv.gz$",
                        full.names = FALSE)
files_names <- file_path_sans_ext(csv_files, compression = TRUE)

for (file_name in files_names) {
  assign(paste0(file_name, "_df"),
         fread(file.path(
           folder_name,
           paste0(file_name, ".csv.gz")
         )))
}

csv_files
```

```{r data_load_clear}
rm(csv_files, file_name)
```

# Data intoduction

The section below presents the datasets used for analysis, including their structure, dimensions, and basic statistics.

```{r overall_statistics, results = 'asis'}
rows_count <- 0
cols_count <- 0
values_count <- 0
non_na_count <- 0

for (file_name in files_names) {
  df_name <- get(paste0(file_name, "_df"))
  
  rows_count <- rows_count + nrow(df_name)
  cols_count <- cols_count + ncol(df_name)
  values_count <- values_count + nrow(df_name) * ncol(df_name)
  non_na_count <- non_na_count + sum(!is.na(df_name))
}

na_percentage <- (values_count - non_na_count) * 100 / values_count

kable(
  data.frame(
    "Rows_count" = rows_count,
    "Columns_count" = cols_count,
    "Values_count" = values_count,
    "NA_percentage" = paste0(round(na_percentage, 2), "%")
  ),
  caption = "Total dataset size",
  align = "c"
)

rm(
  rows_count,
  cols_count,
  values_count,
  non_na_count,
  na_percentage,
  file_name,
  df_name
)
```

## Data structure

```{r data_schema}
include_graphics(file.path(folder_name,
                                  "rebrickable_schema_v3.png"))
```

## Datasets summaries

```{r summaries, results = 'asis'}
options(knitr.kable.NA = '')

for (file_name in files_names) {
  displey_name <- gsub("_", " ", toTitleCase(file_name))
  df_name <- get(paste0(file_name, "_df"))
  summary_table <- unclass(summary(df_name))
  
  cat('\n###', displey_name, '\n')
  
  print(kable(
    data.frame(Rows = dim(df_name)[1], Columns = dim(df_name)[2]),
    caption = paste(displey_name, "dataset dimensions", sep = " "),
    align = "l"
  ))
  
  print(kable(
    data.frame(summary_table, check.names = FALSE),
    row.names = FALSE,
    digits = 2,
    align = "l",
    caption = paste(displey_name, "dataset basic statistics", sep = " "),
  ))
  
  print(kable(
    head(df_name),
    align = "l",
    caption = paste("Head of", displey_name, "dataset", sep = " "),
  ))
  
  cat('\n')
}

rm(file_name, df_name, displey_name, summary_table)
```

# Detailed analysis

## Colors

### Most popular colors of parts

```{r popular_part_colors}
inventory_parts_df %>%
  left_join(colors_df, by = c("color_id" = "id")) %>%
  select(name, rgb) %>%
  mutate(rgb = paste0("#", rgb)) %>%
  group_by(name, rgb) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(desc(count)) %>%
  filter(count > 30000) %>%
  ggplot(aes(
    x = reorder(name, count),
    y = count,
    color = ifelse(rgb == "#FFFFFF", "black", rgb),
    fill = rgb
  )) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_identity() +
  scale_color_identity() +
  scale_y_continuous(
    breaks = seq(0, 200000, by = 50000),
    label = format(seq(0, 200000, by = 50000), big.mark = " ", trim = TRUE)
  ) +
  labs(title = "Most popular colors of parts [> 30,000]",
       x = "Color",
       y = "Number of parts") +
  theme_minimal()
```

### Distribution of colors by transparency

```{r colors_trans}
colors_df %>%
  group_by(is_trans) %>%
  summarise(count = n()) %>%
  mutate(is_trans = ifelse(is_trans == "t", "Transparent", "Opaque")) %>%
  ggplot(aes(x = is_trans, y = count, fill = is_trans)) +
  geom_bar(stat = "identity") +
  labs(title = "Distribution of colors by transparency",
       x = "Transparency",
       y = "Number of transparent colors") +
  geom_text(
    aes(label = count),
    vjust = -0.2,
    color = "black",
    size = 4
  ) +
  theme_minimal()
```

## Elements

### Most popular elements colors

```{r popular_elements_colors}
elements_df %>%
  left_join(colors_df, by = c("color_id" = "id")) %>%
  select(name, rgb) %>%
  mutate(rgb = paste0("#", rgb)) %>%
  group_by(name, rgb) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(desc(count)) %>%
  filter(count > 2000) %>%
  ggplot(aes(
    x = reorder(name, count),
    y = count,
    color = ifelse(rgb == "#FFFFFF", "black", rgb),
    fill = rgb
  )) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_identity() +
  scale_color_identity() +
  labs(title = "Most popular elements colors [> 2000]",
       x = "Color",
       y = "Number of elements") +
  theme_minimal()
```

## Minifigs

### Most popular number of parts used to build minifigs

```{r popular_minifigs_number_of_parts}
minifigs_df %>%
  group_by(num_parts) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(6) %>%
  ggplot(aes(
    x = reorder(num_parts, count),
    y = count,
    fill = num_parts
  )) +
  geom_bar(stat = "identity") +
  labs(title = "Most popular number of parts used to build minifigs",
       x = "Number of parts",
       y = "Number of minifigs") +
  scale_fill_gradient(name = "Number of Parts") +
  theme_minimal()
```

### Most popular minifigs

```{r popular_minifigs}
inventories_df %>%
  inner_join(inventory_minifigs_df, by = c("id" = "inventory_id")) %>%
  inner_join(minifigs_df, by = c("fig_num" = "fig_num")) %>%
  group_by(name, num_parts) %>%
  summarise(count = n(), .groups = "drop") %>%
  mutate(name = str_trunc(name, 30)) %>%
  arrange(desc(count)) %>%
  head(10) %>%
  ggplot(aes(
    x = reorder(name, count),
    y = count,
    fill = num_parts
  )) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_gradient(name = "Number of Parts") +
  labs(title = "Most popular minifigs",
       x = "Minifig name",
       y = "Number of minifigs") +
  theme_minimal()
```

```{r popular_minifigs_table}
inventories_df %>%
  inner_join(inventory_minifigs_df, by = c("id" = "inventory_id")) %>%
  inner_join(minifigs_df, by = c("fig_num" = "fig_num")) %>%
  select(name, img_url) %>%
  group_by(name, img_url) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(desc(count)) %>%
  head(10) %>%
  mutate(img_url = paste0("![](", img_url, "){width=25%}")) %>%
  kable(caption = "Most popular minifigs",
        col.names = c("Name", "Image", "Number of minifigs"),
        align = "c")
```

## Themes

### Most popular themes

```{r most_popular_themes}
sets_df %>%
  left_join(themes_df, by = c("theme_id" = "id")) %>%
  left_join(themes_df, by = c("parent_id" = "id")) %>%
  rename(
    parent_theme_name = name,
    grandparent_id = parent_id.y,
    theme_name = name.y
  ) %>%
  select(parent_theme_name, grandparent_id, theme_name) %>%
  left_join(themes_df, by = c("grandparent_id" = "id")) %>%
  rename(grandarent_theme_name = name) %>%
  select(grandarent_theme_name, parent_theme_name, theme_name) %>%
  mutate(name = ifelse(
    !is.na(grandarent_theme_name),
    grandarent_theme_name,
    ifelse(!is.na(parent_theme_name), parent_theme_name, theme_name)
  )) %>%
  group_by(name) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  filter(count > 500) %>%
  ggplot(aes(
    x = reorder(name, count),
    y = count,
    fill = log(count)
  )) +
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks = seq(0, 3500, by = 500)) +
  guides(fill = FALSE) +
  labs(title = "Most popular themes",
       x = "Theme name",
       y = "Number of sets") +
  coord_flip() +
  theme_minimal()
```

## Parts

### Most popular parts

```{r most_popular_parts}
inventories_df %>%
  inner_join(inventory_parts_df, by = c("id" = "inventory_id")) %>%
  inner_join(parts_df, by = c("part_num" = "part_num")) %>%
  select(name, part_num) %>%
  group_by(name, part_num) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(desc(count)) %>%
  head(10) %>%
  mutate(name = str_trunc(name, 30)) %>%
  ggplot(aes(
    x = reorder(name, count),
    y = count,
    fill = log(count)
  )) +
  scale_y_continuous(
    breaks = seq(0, 125000, by = 25000),
    label = format(seq(0, 125000, by = 25000), big.mark = " ", trim = TRUE)
  ) +
  guides(fill = FALSE) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Most popular parts",
       x = "Part name",
       y = "Number of parts") +
  theme_minimal()
```

```{r most_popular_parts_table}
inventories_df %>%
  inner_join(inventory_parts_df, by = c("id" = "inventory_id")) %>%
  inner_join(parts_df, by = c("part_num" = "part_num")) %>%
  group_by(name, part_num) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(desc(count)) %>%
  head(10) %>%
  inner_join(distinct(inventory_parts_df, part_num, .keep_all = TRUE)) %>%
  select(name, img_url, count) %>%
  mutate(img_url = paste0("![](", img_url, "){width=25%}")) %>%
  kable(
    caption = "Most popular minifigs",
    col.names = c("Name", "Image", "Number of parts"),
    align = "c"
  )
```

### Most populat parts material

```{r most_popular_parts_material}
ggplotly(
inventories_df %>%
  inner_join(inventory_parts_df, by = c("id" = "inventory_id")) %>%
  inner_join(parts_df, by = c("part_num" = "part_num")) %>%
  group_by(part_material) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(percent = round(count / sum(count) * 100, 2)) %>%
  head(10) %>%
  ggplot(aes(
    x = reorder(part_material, percent),
    y = percent,
    fill = percent
  )) +
  guides(fill = FALSE) +
  labs(title = "Most popular parts material",
       x = "Part material",
       y = "Percentage of parts (%)") +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_y_continuous(labels = percent_format(scale = 1)))
```

### Most popular parts categories

```{r most_popular_parts_categories}
ggplotly(
  inventories_df %>%
    inner_join(inventory_parts_df, by = c("id" = "inventory_id")) %>%
    inner_join(parts_df, by = c("part_num" = "part_num")) %>%
    group_by(part_cat_id) %>%
    summarise(count = n()) %>%
    arrange(desc(count)) %>%
    head(10) %>%
    inner_join(part_categories_df, by = c("part_cat_id" = "id")) %>%
    mutate(name = str_trunc(name, 30)) %>%
    ggplot(aes(
      x = reorder(name, count),
      y = count,
      fill = log(count)
    )) +
    guides(fill = FALSE) +
    labs(title = "Most popular parts categories",
         x = "Part category name",
         y = "Number of parts") +
    coord_flip() +
    geom_bar(stat = "identity") +
    theme_minimal()
)
```

## Sets

### Sets with the most parts

```{r sets_with_the_most_parts}
sets_df %>%
  arrange(desc(num_parts)) %>%
  head(10) %>%
  ggplot(aes(
    x = reorder(name, num_parts),
    y = num_parts,
    fill = log(num_parts)
  )) +
  guides(fill = FALSE) +
  labs(title = "Sets with the most parts",
       x = "Set name",
       y = "Number of parts") +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_minimal()
```

```{r sets_with_the_most_parts_table}
sets_df %>%
  arrange(desc(num_parts)) %>%
  head(10) %>%
  select(name, img_url, num_parts) %>%
  mutate(img_url = paste0("![](", img_url, "){width=25%}")) %>%
  kable(
    caption = "Sets with the most parts",
    col.names = c("Name", "Image", "Number of parts"),
    align = "c"
  )
```

# Corelation

## Total number of colors used in the sets and the year

```{r correlation_num_colors_year_df}
cor_num_colors_year_df <- inventories_df %>%
  inner_join(inventory_parts_df, by = c("id" = "inventory_id")) %>%
  inner_join(sets_df, by = c("set_num" = "set_num")) %>%
  select(year, color_id) %>%
  distinct() %>%
  filter(year < 2023) %>%
  group_by(year) %>%
  summarise(count = n())
```

```{r correlation_num_colors_year_table}
cor_num_colors_year_df %>%
  rename("Year" = year, "Number of colors" = count) %>%
  cor %>%
  round(3) %>%
  kable(caption = "Correlation between the total number of colors and the year",
        align = "c")
```

```{r correlation_num_colors_year}
ggplotly(
  cor_num_colors_year_df %>%
    ggplot(aes(x = year, y = count)) +
    geom_point() +
    scale_x_continuous(breaks = seq(1950, 2023, by = 10)) +
    labs(title = "Correlation between the total number of colors and the year",
         x = "Year",
         y = "Number of colors") +
    geom_smooth() +
    theme_minimal()
)
```

```{r correlation_num_colors_year_clear}
rm(cor_num_colors_year_df)
```

## Total number of parts per year and year

```{r correlation_sum_of_part_over_years_df}
cor_sum_of_part_over_years_df <- sets_df %>%
  select (year, num_parts) %>%
  group_by(year) %>%
  summarise(count = sum(num_parts)) %>%
  filter(year < 2023)
```

```{r correlation_sum_of_part_over_years_table}
cor_sum_of_part_over_years_df %>%
  rename("Year" = year, "Total number of parts" = count) %>%
  cor %>%
  round(3) %>%
  kable(caption = "Correlation between total number of parts per year and year of production",
        align = "c")
```

```{r correlation_sum_of_part_over_years}
ggplotly(
  cor_sum_of_part_over_years_df %>%
    ggplot(aes(x = year, y = count)) +
    geom_point() +
    scale_x_continuous(breaks = seq(1950, 2023, by = 10)) +
    scale_y_continuous(
      breaks = seq(0, 280000, by = 50000),
      label = format(seq(0, 280000, by = 50000), big.mark = " ", trim = TRUE)
    ) +
    labs(title = "Correlation between total number of parts per year and year of production",
         x = "Year",
         y = "Total number of parts") +
    geom_smooth() +
    theme_minimal()
)
```

```{r correlation_sum_of_part_over_years_clear}
rm(cor_sum_of_part_over_years_df)
```

## Total number of sets and year

```{r correlation_number_of_sets_df}
cor_number_of_sets_df <- sets_df %>%
  group_by(year) %>%
  summarise(count = n()) %>%
  filter(year < 2023)
```

```{r correlation_number_of_sets_table}
cor_number_of_sets_df %>%
  rename("Year" = year, "Total number of sets" = count) %>%
  cor %>%
  round(3) %>%
  kable(caption = "Correlation between total number of sets and year of production",
        align = "c")
```

```{r correlation_number_of_sets}
ggplotly(
  cor_number_of_sets_df %>%
    ggplot(aes(x = year, y = count)) +
    geom_point() +
    scale_x_continuous(breaks = seq(1950, 2023, by = 10)) +
    labs(title = "Total number of sets over years",
         x = "Year",
         y = "Correlation between total number of sets and year of production") +
    geom_smooth() +
    theme_minimal()
)
```

```{r correlation_number_of_sets_clear}
rm(cor_number_of_sets_df)
```

# Trends

## Number of sets over time for most popular theme

```{r most_popular_themes_over_time, fig.height = 8}
ggplotly (
  sets_df %>%
    left_join(themes_df, by = c("theme_id" = "id")) %>%
    left_join(themes_df, by = c("parent_id" = "id")) %>%
    rename(
      parent_theme_name = name,
      grandparent_id = parent_id.y,
      theme_name = name.y
    ) %>%
    select(year, parent_theme_name, grandparent_id, theme_name) %>%
    left_join(themes_df, by = c("grandparent_id" = "id")) %>%
    rename(grandarent_theme_name = name) %>%
    select(year, grandarent_theme_name, parent_theme_name, theme_name) %>%
    mutate(name = ifelse(
      !is.na(grandarent_theme_name),
      grandarent_theme_name,
      ifelse(!is.na(parent_theme_name), parent_theme_name, theme_name)
    )) %>%
    select(year, name) %>%
    group_by(name, year) %>%
    summarise(count = n(), .groups = "drop") %>%
    filter(
      name %in% c("Gear",
                  "Duplo",
                  "Educational and Dacta",
                  "Books",
                  "Star Wars")
    ) %>%
    filter(year < 2023 & year > 1985) %>%
    ggplot(aes(
      x = year,
      y = count,
      color = name
    )) +
    guides(color = FALSE) +
    geom_point() +
    geom_line() +
    labs(title = "Number of sets over time for each main theme",
         x = "Year",
         y = "Number of sets") +
    facet_grid(name ~ ., scales = "free_y") +
    theme_bw()
)
```

## Mean number of parts over years for themes

```{r number_of_parts_over_time_for_each_theme}
temp_df <- sets_df %>%
    left_join(themes_df, by = c("theme_id" = "id")) %>%
    left_join(themes_df, by = c("parent_id" = "id")) %>%
    rename(
      parent_theme_name = name,
      grandparent_id = parent_id.y,
      theme_name = name.y
    ) %>%
    select(year, parent_theme_name, grandparent_id, theme_name, num_parts) %>%
    left_join(themes_df, by = c("grandparent_id" = "id")) %>%
    rename(grandarent_theme_name = name) %>%
    select(
      year,
      grandarent_theme_name,
      parent_theme_name,
      theme_name,
      num_parts
    ) %>%
    mutate(name = ifelse(
      !is.na(grandarent_theme_name),
      grandarent_theme_name,
      ifelse(!is.na(parent_theme_name), parent_theme_name, theme_name)
    )) %>%
    select(year, name, num_parts) %>%
    group_by(name, year) %>%
    summarise(mean = mean(num_parts), .groups = "drop") %>%
    filter(year < 2023)

names_to_remove <- temp_df %>%
  group_by(name) %>%
  summarise(num_unique_years = n_distinct(year),
            .groups = "drop") %>%
  filter(num_unique_years < 15)

ggplotly (  
  temp_df %>%
    filter(!name %in% names_to_remove$name) %>%
    ggplot(aes(
      x = year,
      y = mean,
      color = name
    )) +
    geom_point() +
    labs(title = "Mean number of parts over years for theme",
         x = "Year",
         y = "Number of parts") +
    theme_minimal()
)

rm(temp_df, names_to_remove)
```

## Trends in sets

```{r sets_trends, fig.height = 8}
ggplotly (
  sets_df %>%
    group_by(year) %>%
    summarise(
      "Max parts" = max(num_parts),
      "Mean parts" = mean(num_parts),
      "Big sets over 1000 parts" = sum(num_parts > 1000),
      "Themes number" = n_distinct(theme_id)
    ) %>%
    filter(year < 2023) %>%
    gather(key = "key", value = "value",-year) %>%
    ggplot(aes(
      x = year, y = value, color = key
    )) +
    geom_line() +
    guides(color = FALSE) +
    labs(title = "Trends in sets over years",
         x = "Year",
         y = "Totals") +
    facet_grid(key ~ ., scales = "free_y") +
    theme_bw()
)
```

# Predictions / Forcasting

TODO
